Query Optimization for Dynamic Imputation

### 2017-03-01 paper/experiments.tex
paper: fix query value ranges
paper: pass over section 4.4.1

\begin{table*}
  \todo{query parameter scaling}
  \centering
  \begin{subtable}{\linewidth}
    \input{queries-cdc}
    \caption{Queries on CDC data}\label{fig:queries-cdc}
  \end{subtable}
  \par\medskip
  \begin{subtable}{\linewidth}
    \input{queries-fcc}
    \caption{Queries on freeCodeCamp data}\label{fig:queries-fcc}
  \end{subtable}
  \par\medskip
  \caption{Queries used in our experiments.}\label{fig:queries}
\end{table*}

@@

We also calculate SMAPE over the number of tuples used to produce the results
in each configuration with respect to the number of tuples satisfying the same query when
the base tables have been imputed. In many cases where the SMAPE reduction between $\alpha = 1$ and
$\alpha = 0$ is small, for example \Cref{q6}\todo{confirm}, we highlight that the count of tuples can be significantly different between
the two scenarios. So while the aggregate used might not have been significantly affected by the different population,
other aggregates may well be. This highlights a challenge for a user handling data imputation traditionally: it is unclear if
the missing data will have a large or small negative impact on their analysis until they have paid the cost of
running it. By using \ProjectName{} this cost can be lowered significantly.

>>>>

\begin{table*}
  \centering
  \begin{subtable}{\linewidth}
    \input{queries-cdc}
    \caption{Queries on CDC data}\label{fig:queries-cdc}
  \end{subtable}
  \par\medskip
  \begin{subtable}{\linewidth}
    \input{queries-fcc}
    \caption{Queries on freeCodeCamp data}\label{fig:queries-fcc}
  \end{subtable}
  \par\medskip
  \caption{Queries used in our experiments.}\label{fig:queries}
\end{table*}

@@

We also calculate the number of tuples used to produce each aggregate output.
The Count columns in \Cref{table:smape} show the percentage difference between the number of tuples in the aggregate for $\alpha = 1$ and $\alpha = 0$ and running the query on the imputed base table.
This shows that when optimizing for performance, not quality, many tuples are dropped.
Even in cases where the SMAPE reduction between $\alpha = 1$ and $\alpha = 0$ is small (\Cref{q2}, \Cref{q6}) the tuple count is significantly different.
In these cases, the aggregate value is not significantly impacted by the missing data.
However, if the missing data is biased then the aggregate will have a significant error.
This highlights a challenge for a user handling data imputation traditionally: it is unclear if the missing data will have a large or small negative impact on their analysis until they have paid the cost of running it.
By using \ProjectName{} this cost can be lowered significantly.
